\documentclass[a4paper,12pt,sans]{moderncv}

\moderncvstyle{casual}
\moderncvcolor{blue}

\usepackage[scale=0.85]{geometry}
\setlength{\hintscolumnwidth}{3.5cm}
\usepackage{multicol}

\moderncvicons{awesome}

\name{Nicola}{Vermeulen}
\title{Curriculum Vit\ae}

\phone[mobile]{+31~63~360~1055}
\email{nicola@lolwut.co.za}
\begin{document}
\makecvtitle

% \cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}

\section{Education}
\cventry{2018--2021(expected)}{B.Sc{} Computer Science}{Vrije Universiteit Amsterdam}{}{}{}
\cventry{2014--2015}{B.Sc.{} Computer Science}{University of Cape Town}{(not completed)}{}{}

\section{Work Experience}
\cventry{Jan 2017--Jan 2018}{Graduate Software Developer}{Booking.com}{}{}{
   Worked on 3 seperate teams that focused on different business areas such as the core website and the hotel management portal  \\
    Technologies: Perl, MySQL, Hadoop, Oozie, Git.
}

\cventry{May 2016--Jan 2017}{Software Engineer}{Takealot.com}{}{}{
    Finished graduate programme and joined the Market Place team. Projects included analysing and rewriting e-commerce platform components for scalability. \\
    Technologies: Python, Pyramid, Swagger, Docker, Git.
}

\cventry{Nov 2015--Feb 2016}{Software Developer Intern}{SimplePay}{}{}{
    Integrated payroll product with Quickbooks Online so that customers can automatically add employee wages to ledgers. \\
    Technologies: Ruby on Rails, Git.
}

\cventry{Jun 2015--Jul 2015}{Software Developer Intern}{Amazon Web Services}{}{}{
    Extended the benchmarking platform to allow finer control over execution;
    wrote scripts for data aggregation. \\
    Technologies: Java, Python, Git.
}

\cventry{Jun 2014--Jul 2014}{Software Development Intern}{BusinessOptics}{}{}{
    Developed an EC2 instance management dashboard to reduce time spent launching and terminating instances. \\
    Technologies: Python, Django, HTML/CSS, AWS, Git.
}


\section{Other Involvement}
\cventry{2014}{Computer Science Class Representative}{University of Cape Town}{}{}{}
\cventry{May 2014}{Team Leader}{Standard Bank IT Challenge}{}{}{Algorithmic programming contest. Placed 4th of 68 in heats.}
\cventry{Oct 2014}{Team Leader}{ACM International Collegiate Programming Contest}{}{}{Placed 6th in South Africa regional contest.}
\cventry{Jan 2015}{Volunteer Tutor}{Code4CT}{}{}{Helped teach underpriviledged girls the basics of web development, HTML, CSS and UI design.}


\end{document}
